---
title: "dumb line graph"
author: "too many cells wearing a suit"
date: "2020 September"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
editor_options:
  chunk_output_type: console
---
### Goals

Make a line graph that is terrible, but still informative

***

### Setup

#### Load packages

```{r, message = FALSE, warning = FALSE, echo = TRUE}
library(dplyr)
library(tidyr)
library(ggplot2)
```

#### Load data

Easy mode, use Iris data

***

# Terrible graph

* Use line graph for discrete, non-sequential variables
    + One axis is a dimension (l or w)
    + One axis is measurement label (sl, sw, pl, pw)
* Too many lines
    + Each observation gets a line
* Color code by species with ugly/harsh colors
* Circlize the x-axis, lol

```{r, message = FALSE, warning = FALSE, echo = TRUE, fig.height = 6, fig.width = 6}
# make iris object for plotting
iris_pt <- iris
iris_pt$obs <- row.names(iris_pt)
iris_pt <- gather(iris_pt, "Sepal.Length", "Sepal.Width", "Petal.Length", "Petal.Width", key = "Dim", value = "Length")

iris_lab <- data.frame(Dim = c("Petal.Length",
                          "Petal.Width",
                          "Sepal.Length",
                          "Sepal.Width"),
                       Length = c(max(iris$Petal.Length) + 1,
                                  max(iris$Petal.Width) + 3,
                                  max(iris$Sepal.Length) + 1,
                                  max(iris$Sepal.Width) + 3),
                       obs = "label")

# make the bad plot, lmao
ggplot(iris_pt, aes(x = Dim, y = Length, color = Species, group = obs)) +
  geom_text(data = iris_lab,
            aes(x = Dim, y = Length, label = Dim),
            color = "white", family = "serif", fontface = "italic") +
  geom_line(alpha = 0.33) +
  scale_color_manual(values = c("#ffcc00", "#ccffcc", "#990066"),
                     guide = guide_legend(override.aes = list(alpha = 1))) +
  scale_y_continuous(limits = c(0, 9),
                     breaks = c(0:9)) +
  coord_polar("x", start= -44.771) +
  theme(panel.background = element_rect(fill = "black"),
        panel.grid.major = element_line(color = "darkgrey",
                                        size = 0.25),
        legend.key = element_rect(fill = "black"),
        axis.text.x = element_blank(),
        text = element_text(family = "serif", face = "italic"))
```